Describing the C-space of asynchronous periodic task using DIT

### 2013-07-23 dit-paper_ieee.tex
First Periodic DIT -> FPDIT
+ removed joke

Keywords: Real-time systems, C-space, WCET

Buzzword: sensitivity analysis
\end{abstract}

@@

		\begin{definition}
			The \textbf{first periodic DIT} of a system is the earliest DIT occurring
			strictly after $O_{max}$.
		\end{definition}

@@

	\subsection{Existence condition}
  \label{sct:FPDITexist}
		As in the synchronous case, the problem of existence of the first periodic DIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall i \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]
		which means that there could be systems with no first periodic DIT.
		We now present an example of such a system.\\

@@

		Here, the possible values of $a_1$ are 3 and 4, and the possible values
		of $a_2$ are 7 and 8. For a first periodic DIT to exist, one of those
		condition must be fulfilled:
		\[
		\left[
		\begin{array}{c}
			3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
		\end{array}
		\right.
		\]
		However those four conditions are false, so the system has no first
		periodic DIT (and no other DIT than $t=0$).

@@

	We wanted to quantify how much systems has a first periodic DIT........

	We generated task systems by
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) equal to 3
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{CDF}, T_i]$, where the $CDF$ is called \emph{Constrained Deadline Factor}.
	\end{itemize}
	and then computed the value of the first periodic DIT.\\

	We use the CDF because........

	The result are represented in Fig. \ref{fig:noFPDIT}

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit.png}
	\end{center}
	\label{fig:noFPDIT}
	\end{figure}

@@

>>>>

Keywords: Real-time systems, C-space, WCET, sensitivity analysis
\end{abstract}

@@

		\begin{definition}
			The \textbf{first periodic DIT} (FPDIT) of a system is the earliest DIT occurring
			strictly after $O_{max}$.
		\end{definition}

@@

	\subsection{Existence condition}
  \label{sct:FPDITexist}
		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\[
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall i \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \; T_i) \\
						a_i \in [D_i, T_i]
					\end{array}
				\right.
			\end{array}
		\]

		This system is guaranteed to have at least one solution modulo $H$ for given
		values of $a_i$ if the following condition is respected:
		\[
			a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i,
			T_j)) \; \forall i,j
		\]
		which means that there could be systems with no FPDIT.
		We now present an example of such a system.\\

@@

		Here, the possible values of $a_1$ are 3 and 4, and the possible values
		of $a_2$ are 7 and 8. For a FPDIT to exist, one of those
		condition must be fulfilled:
		\[
		\left[
		\begin{array}{c}
			3 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			3 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 7 + 2 \; (\operatorname{mod} \; 4 ) \\
			4 + 0 \equiv 8 + 2 \; (\operatorname{mod} \; 4 ) \\
		\end{array}
		\right.
		\]
		However those four conditions are false, so the system has no FPDIT
		(and no other DIT than $t=0$).

@@

	We wanted to quantify how much systems have a FPDIT........

	We generated task systems by
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniSort} algorithm described in \cite{bini2005measuring}, with parameters
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) equal to 3
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20, which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - \frac{T_i - C_i}{CDF}, T_i]$, where the $CDF$ is called \emph{Constrained Deadline Factor}.
	\end{itemize}
	and then computed the value of the FPDIT.\\

	We use the CDF because........\\

	\begin{figure}[h]
	\begin{center}
		\includegraphics[width=0.5\textwidth]{python-simulation/plots/nofpdit.png}
	\end{center}
	\caption{Evolution of the existence of FPDIT with the CDF}
	\label{fig:noFPDIT}
	\end{figure}

	The result are represented in Fig. \ref{fig:noFPDIT}. We observe that the more we are close to the implicit deadline case, the less systems have FPDIT.

@@

!!! (Sans appliquer le simplexe ou un truc comme ça, si un DIT existe on divisera toujours par 4 le nombre de contraintes)
